---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bcspecies 

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

`bcspecies` provides a cleaned BC Species conservation dataset and functions to map distrbution by ecosection and view conservation status for species in British Columbia, Canada.

## Installation

To install the developmental version from [GitHub](https://github.com/GinKampen/bcspecies)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("GinKampen/bcspecies")
```

## Demonstration
View the first 5 species' scientific names in the dataset
```{r}
library(bcspecies)
bc_species$ScientificName[1:5]
```

Map distribution by ecosection of *Anemone occidentalis - Carex nigricans*
```{r}
species <- "Abies grandis / Berberis nervosa"
species_map(species)
```

Get conservation status of *Anemone occidentalis - Carex nigricans*
```{r}
conservation_status(species)
```


## Contribution

Please report any [issues](https://github.com/GinKampen/bcspecies/issues).

[Pull requests](https://github.com/GinKampen/bcspecies/pulls) are always welcome.

### Code of Conduct

Please note that the bcspecies project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/1/0/0/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
